Researchers' perceptions of malaria eradication: findings from a mixed-methodsanalysis of a large online survey

### 2018-04-23 paper.tex
format changes

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Researchers' perceptions of malaria eradication: findings from a mixed-methods analysis of a large online survey},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}
  \title{Researchers' perceptions of malaria eradication: findings from a
mixed-methods analysis of a large online survey}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

@@

Malaria is a parasitic disease transmitted among humans by mosquitoes.
The \emph{Plasmodium falciparum} species accounts for a large majority
of the 200 million annual cases as well as the half million annual
deaths worldwide {[}1{]} {[}2{]} {[}3{]}. Malaria ``elimination'', the
``interruption of all local transmission of the infection in a country
or region'' {[}4{]} is actively being pursued by dozens of countries
around the world, leading to a renewed push for ``eradication'' (``the
worldwide interruption of transmission'') {[}5{]} {[}6{]} {[}7{]}.

This is not the first time that eradication has been in the
international spotlight. The scientific and public health communities
have had eradication on their policy agenda since the World Health
Organisation (WHO) established the Global Malaria Eradication Program in
the 1950s {[}8{]}. In 1957, U.S. President Dwight Eisenhower told
Congress that malaria could be expected to be eradicated in five years.
Following the failure of the WHO's first attempt, the focus shifted away
from global eradication towards local elimination and control
strategies. In recent years, much of the discourse regarding malaria has
shifted back to global eradication {[}9{]}, with funders, researchers,
and public health practitioners rallying to the cause {[}4{]}. The Bill
and Melinda Gates Foundation has begun actively promoting eradication as
feasible ``within a generation'' {[}10{]}, and the WHO has set ambitious
goals, stating the objective of eliminating malaria in 65 new endemic
countries from 2015 through 2030 (Figure 1).

@@

Even in areas of high endemicity, advances in immunology, parasitology,
modeling and vaccinology, along with rapid economic development, have
made eradication appear a more feasible goal, though not possible in the
short term {[}11{]} {[}12{]}. From both administrative {[}13{]} and
scientific {[}14{]} points of view, eradication has never before
received so much attention.

Most of the current research on expert opinion regarding the feasibility
of malaria eradication focuses on the \emph{how} rather than the
\emph{if} and the \emph{when} {[}4{]}. The participants in the Malaria
Eradication Research Agenda (MalERA) process, in particular, have guided
research goals and identified gaps in order for elmination to occur
{[}14{]} {[}6{]}. Though the MalERA authors firmly state that
eradication is \emph{not} feasible given the ``current tools and state
of knowledge'', mentions to the time frame are vague (``within the
lifetime of young scientists just embarking on their careers'' {[}14{]}
and ``in the longer term'' {[}6{]}) and no mention is made of the
perception of the overall probability of achieving eradication.
International programmes, such as the WHO Global Malaria Programme
(GMP), have acknowledged the need ``to take an official position on how
and under what timeline malaria eradication could be achieved''
{[}15{]}. Clarity on timeline and likelihood of eradication could inform
forecasting of disease transmission, and plays a crucial role in the
economic analysis of the expected value of malaria eradication
initiatives, ultimately informing health policy decisions. But achieving
clarity is difficult, given the many complex and interacting variables
which affect malaria transmission, research funding, and technological
development. The question of \emph{how} is complex enough, rendering
questions of \emph{if} and \emph{when} even more difficult to answer.

Proponents of disease eradication point to the success of historical and
current campaigns (smallpox and polio, respectively), and highlight the
long term benefits in health and wealth to future generations {[}16{]}.
One often cited figure is for smallpox eradication, in which the
investment of each dollar led to a return of greater than 400 {[}17{]};
unlike smallpox (for which analysis was able to be retrospectively
constructed based on observed costs and benefits), in the case of a
prevalent disease, forecasting models have to be used in order to
prospectively estimate the value of an investment.
\st{Additionally the estimated impact of malaria on economic indicators is heterogeneous, with singificant impact in areas of Sub-Saharan Africa - where the endemicity is high - and little to no impact in areas of low endemicity}
{[}18{]} {[}19{]}.

The general objective of eradication serves to inspire, rally funder
support, motivate researchers, and focus the efforts of public health
practitioners. But to the extent that malaria eradication (by
definition) has never occurred, the parameters needed for a ex-post
cost-benefit analysis are unknown. Nonetheless, prospectively estimating
eradication's return on investment is crucial to deciding when and how
to pursue the goal, especially in light of the high direct and
opportunity costs of eradication-specific interventions. One approach to
cost-benefit analysis is the use of mathematical and stochastic models.
These have been applied to diseases which are closer to eradication than
malaria, since the uncertainty around model input parameters is less,
requiring fewer cascading assumptions in order to present possible
comparative scenarios. For example, Kastner et al. were able to describe
4 relatively realistic pathways to Lympathic Filariasis eradication, as
well as the pre-requisite role and magnitude of certain interventions
{[}20{]}. A similar modeling framework was then used to estimate the
cost of eradication {[}21{]}. A recent modeling analysis on
onchocerciasis eradication, based on a disease transmission model,
showed that the costs of elimination (relative to staying in ``control
mode'') in Africa would be far lower even in the short term, thanks to
the improvements it would lead to in both treatment times and prevented
surveillance costs. Given the relative proximity of eradication, and the
narrow geographic scope, the authors were also able to estimate the
timeline to eradication {[}22{]}.

This level of detail and specificity in modeling the cost-benefit
landscape of malaria eradication, unfortunately, is not possible (or at
least not commonly undertaken), given its high prevalence and
epidemiological complexity. In fact, there are no mathematical models
(to the authors' knowledge) estimating the likelihood and time frame of
eradication, or its derivative cost-benefit ratio. While a great deal of
rigorous studies exist forecasting the effect of certain tools and
strategies relative to alternatives {[}23{]} or aimed at regional
disease elimination {[}24{]}, these analyses do not endeavor to estimate
the generalization of those tools or strategies to other areas.
Globally, where mathematical modeling has been used for the purposes of
forecasting the future epidemiology of malaria, the methods have
generally been aimed at optimizing elimination methods {[}25{]},
determining whether a strategy is scalable {[}23{]}, guiding funding and
drug development {[}26{]} {[}27{]}, or comparing a range of hypothetical
morbidity scenarios {[}28{]}, rather than assessing the likelihood of or
time until the occurrence of those scenarios. In other words,
researchers are (rightfully) focused on the \emph{how} of eradication,
rather than the forecasting of its timeframe or likelihood, the lack of
attention paid to the latter likely being a reflection of its
complexity, not lack of importance.

To the extent that (i) estimating eradication's likelihood and timeframe
is essential to forecasting the cost-benefit ratio of eradication
interventions, and (ii) mathematical models generally do not venture
into areas of such high uncertainty, alternative methods are needed.
Just as the stock market aggregates perceptions to provide a fairly
accurate assessment of something as complex as a company's value,
aggregating perceptions may be a useful tool for tackling the complexity
of malaria eradication. Many studies have shown value in expert
elicitation as a means to reduce uncertainty and inform decision making
{[}29{]}.
\st{But experts can sometimes be mistaken, a fact implicitly recognized when patients request a "second opinion" from another doctor when facing uncertainty. Additionally, relying on only a small panel of experts for a problem as complex as malaria exposes one to bias, just as an overly concentrated investment portfolio exposes one to more risk.}
As Sir Francis Galton demonstrated in his famous study in which he
showed that the crowds' aggregated estimates of cow's weight formed a
quasi-normal distribution centered around the true weight {[}30{]}
{[}31{]}, averaging the perceptions of many can be more accurate than
taking the opinion of any single expert, since the biases of diverse
viewpoints can be complementary and symbiotic. Measuring consensus and
discord among disease-specific researchers from a variety of disciplines
can serve as a barometer of (informed) opinion, both guiding resources
and identifying areas of concern {[}32{]}.

@@

The survey was intentionally as short as possible, so as to appeal to
time-pressed participants. However, supplementary data on researchers is
of value for the assessing of selection bias and determinants of
perception. Accordingly, we estimated the likelihood of a participant
being of one of two genders (male or female) based on first name. In
order to do this, we used data from the North Atlantic Population
Project, and U.S. government {[}33{]}. We also calculated the total
number of citations which each author had received, as well as the total
number of articles authored. We binned total citations into three
categories: 0-5 (junior-level researchers, PhD students, etc.); 6-99
(most professional academics); and \textgreater{}99 (the most prolific
researchers). The searching and retrieval of information pertaining to
articles and citations from the PubMed database was carried out using
the RISmed package {[}34{]}. Information retrieved about authors was
used to de-bias paramaters in an ordinary least squares regression,
analyzing the association between number of publications and perceived
years to eradication.

@@

Quantitative analysis was carried out in R language {[}35{]}. All
analysis code, as well as the code used for the identification and
contacting of participants, is publicly available at
\url{https://github.com/joebrew/malaria_survey}.

Qualitative analysis of free text comments was carried out using
thematic content analysis, with inductive open coding {[}36{]}.
Participants were invited to provide ``any general comments on the
timeline and likelihood of global eradication''. Thematic content
analysis {[}37{]} was employed to code responses following the 6-phase
approach laid out by Braun and Clarke {[}38{]}. The approach was
inductive, used open-coding to identify latent themes, and underwent
several iterations in which codes were modified, discarded and created.
Using the RQDA software to assist in data management and theme coding
{[}39{]}, four subject themes were identified. Comments were
additionally coded as either descriptive (comments pertaining to the
``problem'' of malaria eradication) or presciptive (pertaining to
potential ``solutions'' for eradicating malaria). Finally, free-text
comments were scored for overall sentiment polarity {[}40{]}.

@@

Eradication of a disease is a ``high stakes game'', exposed to multiple
competing - and at times contradictory - incentives from multiple
stakeholders {[}41{]}. Understanding these incentives, and the factors
which can alter them, is vital to understanding how eradication can
succeed, and where it is most vulnerable to failure. The return on
investment of eradication-specific interventions is affected by the fact
that most researchers agree that eradication will take a long time to
achieve. This, in turn, reduces the expected value of future benefits,
disincentivizing eradication-specific investment. Given this, it is
important to quantify the positive externalities of ``failed''
eradication; in areas of high endemicity, even if the goal of
elimination is not achieved, the reduction in burden or disease can
still make interventions cost-effective.

However, areas of high malaria endemicity are often also those with high
competing health costs. When estimating the return on investment of
malaria elimination initiatives, not only must one take into account the
potential benefits (even in the case of failure), but also the
opportunity costs (even in the case of success). After all, elimination
is not a binary success/failure proposition - an initiative should be
judged both on its epidemiological circumstances {[}42{]} as well as the
counterfactual improvements in health which could have been achieved via
other paths.

@@

This paper has several limitations. Conceptually, academic researchers
are specialists - their narrow, field-specific view of eradication's
feasibility is of arguable reliability, given that they may be
unfamiliar with the operational, cultural and ``real-world'' challenges
of malaria eradication. Though crowds have been found to be more
``wise'' than individuals in many cases, the application of an approach
similar to the ``wisdom of crowds'' is not suitable to all classes of
problems {[}43{]}. Crowds can be susceptible to social biases {[}44{]}
(although this survey's anonimity largely protects against this issue),
and other biases may come in to play, especially given that our study
was of a crowd of ``specialists'', rather than the population as a
whole.

@@

As with Keenan et al's survey of experts regarding the feasibility of
eradication of neglected tropical diseases, our survey detected
relatively high levels of eradication skepticism and did not delve into
whether researchers had clinical or operational experience, nor did it
assess opinions of program workers, nor did it explore complexities
pertaining to different types of or forms of existence of malaria.
Though our sample size was over twice Keenan's, this was largely due to
having contacted more authors, as our response rate was only one fourth
as large {[}32{]}.

@@

\hypertarget{refs}{}
\hypertarget{ref-White2014}{}
{[}1{]} N.J. White, S. Pukrittayakamee, T.T. Hien, M.A. Faiz, O.A.
Mokuolu, A.M. Dondorp, Malaria, The Lancet. 383 (2014) 723--735.
doi:\href{https://doi.org/10.1016/s0140-6736(13)60024-0}{10.1016/s0140-6736(13)60024-0}.

\hypertarget{ref-World2016}{}
{[}2{]} WHO, World Malaria Report, (2016).
\url{http://apps.who.int/iris/bitstream/10665/252038/1/9789241511711-eng.pdf?ua=1}.

\hypertarget{ref-Ashley2018}{}
{[}3{]} E.A. Ashley, A.P. Phyo, C.J. Woodrow, Malaria, The Lancet.
(2018).
doi:\href{https://doi.org/10.1016/s0140-6736(18)30324-6}{10.1016/s0140-6736(18)30324-6}.

\hypertarget{ref-Tanner2015}{}
{[}4{]} M. Tanner, B. Greenwood, C.J.M. Whitty, E.K. Ansah, R.N. Price,
A.M. Dondorp, L. von Seidlein, J.K. Baird, J.G. Beeson, F.J. Fowkes, J.
Hemingway, K. Marsh, F. Osier, Malaria eradication and elimination:
Views on how to translate a vision into reality, BMC Medicine. 13
(2015).
doi:\href{https://doi.org/10.1186/s12916-015-0384-6}{10.1186/s12916-015-0384-6}.

\hypertarget{ref-Hopkins2013}{}
{[}5{]} D.R. Hopkins, Disease eradication, New England Journal of
Medicine. 368 (2013) 54--63.
doi:\href{https://doi.org/10.1056/nejmra1200391}{10.1056/nejmra1200391}.

\hypertarget{ref-Rabinovich_2017}{}
{[}6{]} R.N. Rabinovich, C. Drakeley, A.A. Djimde, B.F. Hall, S.I. Hay,
J. Hemingway, D.C. Kaslow, A. Noor, F. Okumu, R. Steketee, et al.,
MalERA: An updated research agenda for malaria elimination and
eradication, PLOS Medicine. 14 (2017) e1002456.
doi:\href{https://doi.org/10.1371/journal.pmed.1002456}{10.1371/journal.pmed.1002456}.

\hypertarget{ref-TheLancet2011}{}
{[}7{]} T. Lancet, Malaria: Control vs elimination vs eradication, The
Lancet. 378 (2011) 1117.
doi:\href{https://doi.org/10.1016/s0140-6736(11)61489-x}{10.1016/s0140-6736(11)61489-x}.

\hypertarget{ref-Njera2011}{}
{[}8{]} J.A. Nájera, M. González-Silva, P.L. Alonso, Some lessons for
the future from the global malaria eradication programme (19551969),
PLoS Med. 8 (2011) e1000412.
doi:\href{https://doi.org/10.1371/journal.pmed.1000412}{10.1371/journal.pmed.1000412}.

\hypertarget{ref-Roberts2007}{}
{[}9{]} L. Roberts, M. Enserink, MALARIA: Did they really say ...
eradication?, Science. 318 (2007) 1544--1545.
doi:\href{https://doi.org/10.1126/science.318.5856.1544}{10.1126/science.318.5856.1544}.

\hypertarget{ref-Gates2014}{}
{[}10{]} B. Gates, We can eradicate malaria---Within a generation,
Breaking a Fever. (2014).
\url{https://www.gatesnotes.com/Health/Eradicating-Malaria-in-a-Generation}.

>>>>

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Researchers' perceptions of malaria eradication: findings from a mixed-methodsanalysis of a large online survey},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}
  \title{Researchers' perceptions of malaria eradication: findings from a
mixed-methodsanalysis of a large online survey}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

@@

Malaria is a parasitic disease transmitted among humans by mosquitoes.
The \emph{Plasmodium falciparum} species accounts for a large majority
of the 200 million annual cases as well as the half million annual
deaths worldwide (White et al., 2014) (WHO, 2016) (Ashley et al., 2018).
Malaria ``elimination'', the ``interruption of all local transmission of
the infection in a country or region'' (Tanner et al., 2015) is actively
being pursued by dozens of countries around the world, leading to a
renewed push for ``eradication'' (``the worldwide interruption of
transmission'') (Hopkins, 2013) (Rabinovich et al., 2017) (Lancet,
2011).

This is not the first time that eradication has been in the
international spotlight. The scientific and public health communities
have had eradication on their policy agenda since the World Health
Organisation (WHO) established the Global Malaria Eradication Program in
the 1950s (Nájera et al., 2011). In 1957, U.S. President Dwight
Eisenhower told Congress that malaria could be expected to be eradicated
in five years. Following the failure of the WHO's first attempt, the
focus shifted away from global eradication towards local elimination and
control strategies. In recent years, much of the discourse regarding
malaria has shifted back to global eradication (Roberts and Enserink,
2007), with funders, researchers, and public health practitioners
rallying to the cause (Tanner et al., 2015). The Bill and Melinda Gates
Foundation has begun actively promoting eradication as feasible ``within
a generation'' (Gates, 2014), and the WHO has set ambitious goals,
stating the objective of eliminating malaria in 65 new endemic countries
from 2015 through 2030 (Figure 1).

@@

Even in areas of high endemicity, advances in immunology, parasitology,
modeling and vaccinology, along with rapid economic development, have
made eradication appear a more feasible goal, though not possible in the
short term (Snow, 2015) (Eckhoff et al., 2014). From both administrative
(Yamey, 2004) and scientific (Alonso et al., 2011) points of view,
eradication has never before received so much attention.

Most of the current research on expert opinion regarding the feasibility
of malaria eradication focuses on the \emph{how} rather than the
\emph{if} and the \emph{when} (Tanner et al., 2015). The participants in
the Malaria Eradication Research Agenda (MalERA) process, in particular,
have guided research goals and identified gaps in order for elmination
to occur (Alonso et al., 2011) (Rabinovich et al., 2017). Though the
MalERA authors firmly state that eradication is \emph{not} feasible
given the ``current tools and state of knowledge'', mentions to the time
frame are vague (``within the lifetime of young scientists just
embarking on their careers'' (Alonso et al., 2011) and ``in the longer
term'' (Rabinovich et al., 2017)) and no mention is made of the
perception of the overall probability of achieving eradication.
International programmes, such as the WHO Global Malaria Programme
(GMP), have acknowledged the need ``to take an official position on how
and under what timeline malaria eradication could be achieved''
(``Malaria policy advisory committee to the WHO,'' 2015). Clarity on
timeline and likelihood of eradication could inform forecasting of
disease transmission, and plays a crucial role in the economic analysis
of the expected value of malaria eradication initiatives, ultimately
informing health policy decisions. But achieving clarity is difficult,
given the many complex and interacting variables which affect malaria
transmission, research funding, and technological development. The
question of \emph{how} is complex enough, rendering questions of
\emph{if} and \emph{when} even more difficult to answer.

Proponents of disease eradication point to the success of historical and
current campaigns (smallpox and polio, respectively), and highlight the
long term benefits in health and wealth to future generations (Barrett,
2013). One often cited figure is for smallpox eradication, in which the
investment of each dollar led to a return of greater than 400 (Barrett,
2006); unlike smallpox (for which analysis was able to be
retrospectively constructed based on observed costs and benefits), in
the case of a prevalent disease, forecasting models have to be used in
order to prospectively estimate the value of an investment.
\st{Additionally the estimated impact of malaria on economic indicators is heterogeneous, with singificant impact in areas of Sub-Saharan Africa - where the endemicity is high - and little to no impact in areas of low endemicity}
(Cutler et al., 2010) (Barofsky et al., 2015).

The general objective of eradication serves to inspire, rally funder
support, motivate researchers, and focus the efforts of public health
practitioners. But to the extent that malaria eradication (by
definition) has never occurred, the parameters needed for a ex-post
cost-benefit analysis are unknown. Nonetheless, prospectively estimating
eradication's return on investment is crucial to deciding when and how
to pursue the goal, especially in light of the high direct and
opportunity costs of eradication-specific interventions. One approach to
cost-benefit analysis is the use of mathematical and stochastic models.
These have been applied to diseases which are closer to eradication than
malaria, since the uncertainty around model input parameters is less,
requiring fewer cascading assumptions in order to present possible
comparative scenarios. For example, Kastner et al. were able to describe
4 relatively realistic pathways to Lympathic Filariasis eradication, as
well as the pre-requisite role and magnitude of certain interventions
(Kastner et al., 2015). A similar modeling framework was then used to
estimate the cost of eradication (Kastner et al., 2017). A recent
modeling analysis on onchocerciasis eradication, based on a disease
transmission model, showed that the costs of elimination (relative to
staying in ``control mode'') in Africa would be far lower even in the
short term, thanks to the improvements it would lead to in both
treatment times and prevented surveillance costs. Given the relative
proximity of eradication, and the narrow geographic scope, the authors
were also able to estimate the timeline to eradication (Kim et al.,
2017).

This level of detail and specificity in modeling the cost-benefit
landscape of malaria eradication, unfortunately, is not possible (or at
least not commonly undertaken), given its high prevalence and
epidemiological complexity. In fact, there are no mathematical models
(to the authors' knowledge) estimating the likelihood and time frame of
eradication, or its derivative cost-benefit ratio. While a great deal of
rigorous studies exist forecasting the effect of certain tools and
strategies relative to alternatives (Brady et al., 2017) or aimed at
regional disease elimination (Kim et al., 2015), these analyses do not
endeavor to estimate the generalization of those tools or strategies to
other areas. Globally, where mathematical modeling has been used for the
purposes of forecasting the future epidemiology of malaria, the methods
have generally been aimed at optimizing elimination methods (Slater et
al., 2015), determining whether a strategy is scalable (Brady et al.,
2017), guiding funding and drug development (Patouillard et al., 2017)
(Slater et al., 2017), or comparing a range of hypothetical morbidity
scenarios (Winskill et al., 2017), rather than assessing the likelihood
of or time until the occurrence of those scenarios. In other words,
researchers are (rightfully) focused on the \emph{how} of eradication,
rather than the forecasting of its timeframe or likelihood, the lack of
attention paid to the latter likely being a reflection of its
complexity, not lack of importance.

To the extent that (i) estimating eradication's likelihood and timeframe
is essential to forecasting the cost-benefit ratio of eradication
interventions, and (ii) mathematical models generally do not venture
into areas of such high uncertainty, alternative methods are needed.
Just as the stock market aggregates perceptions to provide a fairly
accurate assessment of something as complex as a company's value,
aggregating perceptions may be a useful tool for tackling the complexity
of malaria eradication. Many studies have shown value in expert
elicitation as a means to reduce uncertainty and inform decision making
(Morgan, 2014).
\st{But experts can sometimes be mistaken, a fact implicitly recognized when patients request a "second opinion" from another doctor when facing uncertainty. Additionally, relying on only a small panel of experts for a problem as complex as malaria exposes one to bias, just as an overly concentrated investment portfolio exposes one to more risk.}
As Sir Francis Galton demonstrated in his famous study in which he
showed that the crowds' aggregated estimates of cow's weight formed a
quasi-normal distribution centered around the true weight (Wallis, 2014)
(Galton, 1907), averaging the perceptions of many can be more accurate
than taking the opinion of any single expert, since the biases of
diverse viewpoints can be complementary and symbiotic. Measuring
consensus and discord among disease-specific researchers from a variety
of disciplines can serve as a barometer of (informed) opinion, both
guiding resources and identifying areas of concern (Keenan et al.,
2013).

@@

The survey was intentionally as short as possible, so as to appeal to
time-pressed participants. However, supplementary data on researchers is
of value for the assessing of selection bias and determinants of
perception. Accordingly, we estimated the likelihood of a participant
being of one of two genders (male or female) based on first name. In
order to do this, we used data from the North Atlantic Population
Project, and U.S. government (Mullen, 2015). We also calculated the
total number of citations which each author had received, as well as the
total number of articles authored. We binned total citations into three
categories: 0-5 (junior-level researchers, PhD students, etc.); 6-99
(most professional academics); and \textgreater{}99 (the most prolific
researchers). The searching and retrieval of information pertaining to
articles and citations from the PubMed database was carried out using
the RISmed package (Kovalchik, 2015). Information retrieved about
authors was used to de-bias paramaters in an ordinary least squares
regression, analyzing the association between number of publications and
perceived years to eradication.

@@

Quantitative analysis was carried out in R language (R Core Team, 2015).
All analysis code, as well as the code used for the identification and
contacting of participants, is publicly available at
\url{https://github.com/joebrew/malaria_survey}.

Qualitative analysis of free text comments was carried out using
thematic content analysis, with inductive open coding (Markey et al.,
2014). Participants were invited to provide ``any general comments on
the timeline and likelihood of global eradication''. Thematic content
analysis (Vaismoradi et al., 2016) was employed to code responses
following the 6-phase approach laid out by Braun and Clarke (Braun and
Clarke, 2006). The approach was inductive, used open-coding to identify
latent themes, and underwent several iterations in which codes were
modified, discarded and created. Using the RQDA software to assist in
data management and theme coding (Huang, 2017), four subject themes were
identified. Comments were additionally coded as either descriptive
(comments pertaining to the ``problem'' of malaria eradication) or
presciptive (pertaining to potential ``solutions'' for eradicating
malaria). Finally, free-text comments were scored for overall sentiment
polarity (Rinker, 2017).

@@

Eradication of a disease is a ``high stakes game'', exposed to multiple
competing - and at times contradictory - incentives from multiple
stakeholders (Barrett, 2007). Understanding these incentives, and the
factors which can alter them, is vital to understanding how eradication
can succeed, and where it is most vulnerable to failure. The return on
investment of eradication-specific interventions is affected by the fact
that most researchers agree that eradication will take a long time to
achieve. This, in turn, reduces the expected value of future benefits,
disincentivizing eradication-specific investment. Given this, it is
important to quantify the positive externalities of ``failed''
eradication; in areas of high endemicity, even if the goal of
elimination is not achieved, the reduction in burden or disease can
still make interventions cost-effective.

However, areas of high malaria endemicity are often also those with high
competing health costs. When estimating the return on investment of
malaria elimination initiatives, not only must one take into account the
potential benefits (even in the case of failure), but also the
opportunity costs (even in the case of success). After all, elimination
is not a binary success/failure proposition - an initiative should be
judged both on its epidemiological circumstances (Churcher et al., 2014)
as well as the counterfactual improvements in health which could have
been achieved via other paths.

@@

This paper has several limitations. Conceptually, academic researchers
are specialists - their narrow, field-specific view of eradication's
feasibility is of arguable reliability, given that they may be
unfamiliar with the operational, cultural and ``real-world'' challenges
of malaria eradication. Though crowds have been found to be more
``wise'' than individuals in many cases, the application of an approach
similar to the ``wisdom of crowds'' is not suitable to all classes of
problems (Mannes et al., 2014). Crowds can be susceptible to social
biases (Lorenz et al., 2011) (although this survey's anonimity largely
protects against this issue), and other biases may come in to play,
especially given that our study was of a crowd of ``specialists'',
rather than the population as a whole.

@@

As with Keenan et al's survey of experts regarding the feasibility of
eradication of neglected tropical diseases, our survey detected
relatively high levels of eradication skepticism and did not delve into
whether researchers had clinical or operational experience, nor did it
assess opinions of program workers, nor did it explore complexities
pertaining to different types of or forms of existence of malaria.
Though our sample size was over twice Keenan's, this was largely due to
having contacted more authors, as our response rate was only one fourth
as large (Keenan et al., 2013).

@@

\hypertarget{refs}{}
\hypertarget{ref-Alonso2011}{}
Alonso, P.L., Brown, G., Arevalo-Herrera, M., Binka, F., Chitnis, C.,
Collins, F., Doumbo, O.K., Greenwood, B., Hall, B.F., Levine, M.M.,
Mendis, K., Newman, R.D., Plowe, C.V., Rodríguez, M.H., Sinden, R.,
Slutsker, L., Tanner, M., 2011. A research agenda to underpin malaria
eradication. PLoS Med 8, e1000406.
\url{https://doi.org/10.1371/journal.pmed.1000406}

\hypertarget{ref-Ashley2018}{}
Ashley, E.A., Phyo, A.P., Woodrow, C.J., 2018. Malaria. The Lancet.
\url{https://doi.org/10.1016/s0140-6736(18)30324-6}

\hypertarget{ref-Barofsky2015}{}
Barofsky, J., Anekwe, T.D., Chase, C., 2015. Malaria eradication and
economic outcomes in sub-saharan africa: Evidence from uganda. Journal
of Health Economics 44, 118--136.
\url{https://doi.org/10.1016/j.jhealeco.2015.08.002}

\hypertarget{ref-Barrett2013}{}
Barrett, S., 2013. Economic considerations for the eradication endgame.
Philosophical Transactions of the Royal Society B: Biological Sciences
368, 20120149--20120149. \url{https://doi.org/10.1098/rstb.2012.0149}

\hypertarget{ref-barrett}{}
Barrett, S., 2007. Why cooperate? The incentive to supply global public
goods. Oxford University Press.

\hypertarget{ref-Barrett_2006}{}
Barrett, S., 2006. The smallpox eradication game. Public Choice 130,
179--207. \url{https://doi.org/10.1007/s11127-006-9079-z}

\hypertarget{ref-Brady2017}{}
Brady, O.J., Slater, H.C., Pemberton-Ross, P., Wenger, E., Maude, R.J.,
Ghani, A.C., Penny, M.A., Gerardin, J., White, L.J., Chitnis, N., Aguas,
R., Hay, S.I., Smith, D.L., Stuckey, E.M., Okiro, E.A., Smith, T.A.,
Okell, L.C., 2017. Role of mass drug administration in elimination of
plasmodium falciparum malaria: A consensus modelling study. The Lancet
Global Health 5, e680--e687.
\url{https://doi.org/10.1016/s2214-109x(17)30220-6}

\hypertarget{ref-Braun2006}{}
Braun, V., Clarke, V., 2006. Using thematic analysis in psychology.
Qualitative Research in Psychology 3, 77--101.
\url{https://doi.org/10.1191/1478088706qp063oa}

\hypertarget{ref-Churcher_2014}{}
Churcher, T.S., Cohen, J.M., Novotny, J., Ntshalintshali, N., Kunene,
S., Cauchemez, S., 2014. Measuring the path toward malaria elimination.
Science 344, 1230--1232. \url{https://doi.org/10.1126/science.1251449}

\hypertarget{ref-Cutler_2010}{}
Cutler, D., Fung, W., Kremer, M., Singhal, M., Vogl, T., 2010.
Early-life malaria exposure and adult outcomes: Evidence from malaria
eradication in india. American Economic Journal: Applied Economics 2,
72--94. \url{https://doi.org/10.1257/app.2.2.72}

\hypertarget{ref-Eckhoff2014}{}
Eckhoff, P.A., Bever, C.A., Gerardin, J., Wenger, E.A., 2014. Fun with
maths: Exploring implications of mathematical models for malaria
eradication. Malar J 13, 486.
\url{https://doi.org/10.1186/1475-2875-13-486}

\hypertarget{ref-Galton1907Voxpopuli}{}
Galton, F., 1907. Vox populi. Nature 75, 7.
\url{https://doi.org/10.1038/075450a0}

\hypertarget{ref-Gates2014}{}
Gates, B., 2014. We can eradicate malaria---Within a generation.
Breaking a Fever.
